|                       |
|-----------------------|
| title: "stmgame"      |
| author: "minwoo ahn"  |
| date: "2023-08-03"    |
| output: html_document |

```{r}
knitr::opts_chunk$set(echo = TRUE)
```

\##<https://github.com/dondealban/learning-stm>

1.  Groundwater Game ##lag communication

```{r}
library(dplyr)

#add new column that shows sales for previous day
GGcommunicationdataset_mw_060723$lag_communication <- dplyr::lag(GGcommunicationdata_mw_060723$text)

```

## stm installation

```{r}
library(stm)
library (igraph)
library (stmCorrViz)
```

##open in Window or MAC

```{r}
##revise the code as necessary
data <- read.csv("GGcommunicationdata_mw_060723.csv")
```

##stemming and stopword removal

```{r}
processed <- textProcessor(GGcommunicationdataset_mw_062723$text, metadata = GGcommunicationdataset_mw_062723)
```

##structure and index the data for usage in the stm

```{r}
out <- prepDocuments(processed$documents, processed$vocab, processed$meta)
```

##save the output object meta, documents, and vocab into variables

```{r}
docs <- out$documents
vocab <- out$vocab
meta <- out$meta
```

##check removed words and documents

```{r}
plotRemoved(processed$documents, lower.thresh = seq(1,200, by=100))
```

##estimation (1).prevalance of topics across documents' meta data

```{r}
ggfit <- stm(out$documents, out$vocab, K=5, prevalence = ~treatment, data = out$meta, max.em.its=75, init.type = "Spectral", seed = 8458150)

ggfit <- stm(out$documents, out$vocab, K=5, prevalence = ~cooperation+round, data = out$meta, init.type = "Spectral", seed = 8458150)

```

##plot the model

```{r}
plot(ggfit, type = "summary", xlim = c(0,1))
plot(communicationfit2, type = "summary", xlim = c(0,1))
```

##frequent words in topics

```{r}
plot(ggfit, type = "labels", topics = c(3,4))
plot(ggfit, type = "labels", topics = c(1,2))
plot(ggfit, type = "labels", topics = c(5))

```

##histrogram of topics

```{r}
plot(ggfit, type = "hist")
plot(communicationfit2, type = "hist")
```

##comparison of two topics

```{r}
plot(communicationfit, type = "perspectives", topics = c(2,4))
plot(communicationfit, type = "perspectives", topics = c(1,4))
```

##evaluate

```{r}
communicationSelect <- selectModel(out$documents, out$vocab, K=10, prevalence = ~cooperation+round, max.em.its=30, data = meta, runs=20, seed=8458159)
```

##plot different models

```{r}
plotModels(communicationSelect)

```

##plot topic quality

```{r}
topicQuality(model = ggfit, documents = docs)
topicQuality(model = communicationfit2, documents = docs)
```

##label top words

```{r}
labelTopicsSel <- labelTopics(communicationfit, c(1,3,4))
print(sageLabels(communicationfit))
```

##exemplary quote

```{r}
topic4 <- findThoughts(ggfit, texts=, topics = 4, n=3)
plot(topic4)
```

##choose model 3

```{r}
selectModel1 <- communicationSelect$runout [[1]]
```

##estimation

```{r}
out$meta$rating <- as.factor(out$meta$rating)
prep <- estimateEffect(1:5 ~ treatment, communicationfit, meta=out$meta, uncertainty="Global")
prep1 <- estimateEffect(1:5 ~ cooperation+round, ggfit, meta=out$meta, uncertainty="Global")

```

##plotting 1. the effect of scientific uncertainty on communication strategies

```{r}
plot(prep1, covariate="cooperation", topics=c(1,2,4), model=ggfit, method = "difference", cov.value1 = "0", cov.value2 = "1", xlab =  "less cooperation ... more cooperation", main = "The Effects of Communication of Cooperation", labeltype = "custom", custom.labels = c("commit+team chemistry","collaborative caution", "collaborative strategy"))
                                                                                
```

##plotting 2. the effect of communication on cooperation

```{r}
plot(prep1, covariate="cooperation", topics = c(1,2,3,4,5), model=communicationfit, method = "difference", cov.value1 = "0", cov.value2 = "1", xlab = "less cooperation ... more cooperation", main = "The effects of communication on cooperation", xlim = c(-0.5,.5), labeltype = "custom", custom.labels = c("strategy1", "strategy2", "strategy3", "strategy4", "strategy5"))
```

##how prevalence of topics differ across values of a continuous covariate

```{r}
plot(prep1, "round", method="continuous", topics=1, model=ggfit, printlegend=FALSE, xaxt="n", xlab="round (1-10)")
plot(prep1, "round", method="continuous", topics=2, model=ggfit, printlegend=FALSE, xaxt="n", xlab="round (1-10)")
plot(prep1, "round", method="continuous", topics=4, model=ggfit, printlegend=FALSE, xaxt="n", xlab="round (1-10)")
```

##topic corelation

```{r}
mod.out.corr <- topicCorr(communicationfit)
plot(mod.out.corr)
mod.out.corr <- topicCorr(communicationfit2)
plot(mod.out.corr)
```

2.  POM

## stm installation

```{r}
library(stm)
library (igraph)
library (stmCorrViz)
```

##open in Window or MAC

```{r}
##revise the code as necessary
data <- read.csv("GGcommunicationdata_mw_060723.csv")
```

##select POM

```{r}
POMdat <- subset(X4gamesdata_070123, Game == "POM")
```

##stemming and stopword removal

```{r}
processed <- textProcessor(pom_080323$text, metadata = pom_080323)
```

##structure and index the data for usage in the stm

```{r}
out <- prepDocuments(processed$documents, processed$vocab, processed$meta)
```

##save the output object meta, documents, and vocab into variables

```{r}
docs <- out$documents
vocab <- out$vocab
meta <- out$meta
```

##check removed words and documents

```{r}
plotRemoved(processed$documents, lower.thresh = seq(1,200, by=100))
```

##estimation (1).prevalance of topics across documents' meta data

```{r}
pomfit <- stm(out$documents, out$vocab, K=5, prevalence = ~Cooperation_index+round, data = out$meta, max.em.its=75, init.type = "Spectral", seed = 8458150)
```

##plot the model

```{r}
plot(pomfit, type = "summary", xlim = c(0,1))
```

##frequent words in topics

```{r}
plot(pomfit, type = "labels", topics = c(4,2))
```

##histrogram of topics

```{r}
plot(pomfit, type = "hist")
```

##comparison of two topics

```{r}
plot(pomfit, type = "perspectives", topics = c(2,3))
```

##evaluate

```{r}
pomselect <- selectModel(out$documents, out$vocab, K=10, prevalence = ~Cooperation_index+round, max.em.its=30, data = meta, runs=20, seed=8458159)
```

##plot different models

```{r}
plotModels(pomselect)

```

##plot topic quality

```{r}
topicQuality(model = pomfit, documents = docs)
```

##label top words

```{r}
labelTopicsSel <- labelTopics(pomfit, c(3,4))
print(sageLabels(pomfit))
```

##exemplary quote

```{r}
thoughts3 <- findThoughts(communicationfit, texts=text, n=3, topics=3)$docs[[1]]
plotQuote(thoughts3, width=40, main="Topic 3")
```

##choose model 3

```{r}
selectModel1 <- pomselect$runout [[1]]
```

##estimation

```{r}
prep <- estimateEffect(1:5 ~ Cooperation_index+round, pomfit, meta=out$meta, uncertainty="Global")

```

##plotting 1. the effect of communication on cooperation

```{r}
plot(prep, covariate="Cooperation_index", topics = c(2, 4), model=pomfit, method = "difference", cov.value1 = "0", cov.value2 = "2", xlab = "less cooperation ... more cooperation", main = "The effects of communication on cooperation", xlim = c(-0.5,.5), labeltype = "custom", custom.labels = c("system health", "trade"))
```

##how prevalence of topics differ across values of a continuous covariate

```{r}
##system health
plot(prep, "round", method="continuous", topics=2, model=z, printlegend=FALSE, xaxt="n", 
     xlab="round (1-10)")
##trade
plot(prep, "round", method="continuous", topics=4, model=z, printlegend=FALSE, xaxt="n", 
     xlab="round (1-10)")
```

##topic corelation

```{r}
mod.out.corr <- topicCorr(pomfit)
plot(mod.out.corr)
```

#3.irrigation game \## stm installation

```{r}
library(stm)
library (igraph)
library (stmCorrViz)
```

##open in Window or MAC

```{r}
##revise the code as necessary
data <- read.csv("GGcommunicationdata_mw_060723.csv")
```

##stemming and stopword removal

```{r}
processed <- textProcessor(IR080323$text, metadata = IR080323)
```

##structure and index the data for usage in the stm

```{r}
out <- prepDocuments(processed$documents, processed$vocab, processed$meta)
```

##save the output object meta, documents, and vocab into variables

```{r}
docs <- out$documents
vocab <- out$vocab
meta <- out$meta
```

##check removed words and documents

```{r}
plotRemoved(processed$documents, lower.thresh = seq(1,200, by=100))
```

##estimation (1).prevalance of topics across documents' meta data

```{r}
IRfit <- stm(out$documents, out$vocab, K=5, prevalence = ~Cooperation_index+round, data = out$meta, max.em.its=75, init.type = "Spectral", seed = 8458150)
```

##plot the model

```{r}
plot(IRfit, type = "summary", xlim = c(0,1))
```

##frequent words in topics

```{r}
plot(IRfit, type = "labels", topics = c(4,1))
```

##histrogram of topics

```{r}
plot(IRfit, type = "hist")
```

##comparison of two topics

```{r}
plot(IRfit, type = "perspectives", topics = c(1,3))
```

##evaluate

```{r}
IRselect <- selectModel(out$documents, out$vocab, K=10, prevalence = ~Cooperation_index+round, max.em.its=30, data = meta, runs=20, seed=8458159)
```

##plot different models

```{r}
plotModels(IRselect)

```

##plot topic quality

```{r}
topicQuality(model = IRfit, documents = docs)
```

##label top words

```{r}
labelTopicsSel <- labelTopics(IRfit, c(1,4))
print(sageLabels(IRfit))
```

##exemplary quote

```{r}
thoughts2 <- findThoughts(IRfit, texts=text, n=3, topics=2)$docs[[1]]
plotQuote(thoughts3, width=40, main="Topic 2")
```

##choose model 3

```{r}
selectModel2 <- IRselect$runout [[2]]
```

##estimation

```{r}
prep <- estimateEffect(1:5 ~ Cooperation_index+round, IRfit, meta=out$meta, uncertainty="Global")

```

##plotting 1. the effect of communication on cooperation

```{r}
plot(prep, covariate="Cooperation_index", topics = c(1,2,4), model=IRfit, method = "difference", cov.value1 = "0", cov.value2 = "2", xlab = "less cooperation ... more cooperation", main = "The effects of communication on cooperation", xlim = c(-0.5,.5), labeltype = "custom", custom.labels = c("open close", "invest token", "water round"))
```

##how prevalence of topics differ across values of a continuous covariate

```{r}
##system health
plot(prep, "round", method="continuous", topics=1, model=z, printlegend=FALSE, xaxt="n", 
     xlab="round (1-10)")
##trade
plot(prep, "round", method="continuous", topics=2, model=z, printlegend=FALSE, xaxt="n", 
     xlab="round (1-10)")
```

##topic corelation

```{r}
mod.out.corr <- topicCorr(pomfit)
plot(mod.out.corr)
```

#3. foraging game

##installation

```{r}
library(stm)
library (igraph)
library (stmCorrViz)
```

##open in Window or MAC

```{r}
##revise the code as necessary
data <- read.csv("GGcommunicationdata_mw_060723.csv")
```

##stemming and stopword removal

```{r}
processed <- textProcessor(FOR080723$text, metadata = FOR080723)
```

##structure and index the data for usage in the stm

```{r}
out <- prepDocuments(processed$documents, processed$vocab, processed$meta)
```

##save the output object meta, documents, and vocab into variables

```{r}
docs <- out$documents
vocab <- out$vocab
meta <- out$meta
```

##check removed words and documents

```{r}
plotRemoved(processed$documents, lower.thresh = seq(1,200, by=100))
```

##estimation (1).prevalance of topics across documents' meta data

```{r}
FORfit <- stm(out$documents, out$vocab, K=5, prevalence = ~Cooperation_index+round, data = out$meta, init.type = "Spectral", seed = 8458150)
```

##plot the model

```{r}
plot(FORfit, type = "summary", xlim = c(0,1))
```

##frequent words in topics

```{r}
plot(FORfit, type = "labels", topics = c(3,4))
plot(FORfit, type = "labels", topics = c(2,5))
```

##histrogram of topics

```{r}
plot(FORfit, type = "hist")
```

##comparison of two topics

```{r}
plot(FORfit, type = "perspectives", topics = c(3,4))
plot(FORfit, type = "perspectives", topics = c(2,5))
```

##evaluate

```{r}
FORselect <- selectModel(out$documents, out$vocab, K=10, prevalence = ~Cooperation_index+round, data = meta, seed=8458159)
```

##plot different models

```{r}
plotModels(FORselect)

```

##plot topic quality

```{r}
topicQuality(model = FORfit, documents = docs)
```

##label top words

```{r}
labelTopicsSel <- labelTopics(FORfit, c(1,4))
print(sageLabels(FORfit))
```

##exemplary quote

```{r}
thoughts2 <- findThoughts(IRfit, texts=text, n=3, topics=2)$docs[[1]]
plotQuote(thoughts3, width=40, main="Topic 2")
```

##choose model 1

```{r}
selectModel1 <- FORselect$runout [[1]]
```

##estimation

```{r}
prep <- estimateEffect(1:5 ~ Cooperation_index+round, FORfit, meta=out$meta, uncertainty="Global")

```

##plotting 1. the effect of communication on cooperation

```{r}
plot(prep, covariate="Cooperation_index", topics = c(2,3,4), model=FORfit, method = "difference", cov.value1 = "200", cov.value2 = "500", xlab = "less cooperation ... more cooperation", main = "The effects of communication on cooperation", labeltype = "custom", custom.labels = c("collaborative strategy", "collaborative caution", "commit + chemistry"))
```

##how prevalence of topics differ across values of a continuous covariate

```{r}
##commitment
plot(prep, "round", method="continuous", topics=2, model=z, printlegend=FALSE, xaxt="n", 
     xlab="round (1-10)")
##collaborative strategy
plot(prep, "round", method="continuous", topics=3, model=z, printlegend=FALSE, xaxt="n", 
     xlab="round (1-10)")
##collaborative caution
plot(prep, "round", method="continuous", topics=4, model=z, printlegend=FALSE, xaxt="n", 
     xlab="round (1-10)")
```

##topic corelation

```{r}
mod.out.corr <- topicCorr(FORfit)
plot(mod.out.corr)
```
