---
title: "stmgame"
author: "minwoo ahn"
date: "2023-06-07"
output: html_document
------
```{r}
knitr::opts_chunk$set(echo = TRUE)
```
##https://github.com/dondealban/learning-stm


##lag communication
```{r}
library(dplyr)

#add new column that shows sales for previous day
GGcommunicationdata_mw_060723$lag_communication <- dplyr::lag(GGcommunicationdata_mw_060723$text)

```

## stm installation
```{r}
library(stm)
library (igraph)
library (stmCorrViz)
```

##open in MAC
```{r}
data <- read.csv("GGcommunicationdata_mw_060723.csv")
```

##stemming and stopword removal
```{r}
processed <- textProcessor(GGcommunicationdata_mw_060723$lag_communication, metadata = GGcommunicationdata_mw_060723)
```

##structure and index the data for usage in the stm
```{r}
out <- prepDocuments(processed$documents, processed$vocab, processed$meta)
```

##save the output object meta, documents, and vocab into variables
```{r}
docs <- out$documents
vocab <- out$vocab
meta <- out$meta
```

##check removed words and documents
```{r}
plotRemoved(processed$documents, lower.thresh = seq(1,200, by=100))
```

##estimation (1).prevalance of topics across documents' meta data
```{r}
communicationfit <- stm(out$documents, out$vocab, K=5, prevalence = ~treatment, data = out$meta, max.em.its=75, init.type = "Spectral", seed = 8458150)

```
##plot the model
```{r}
plot(communicationfit, type = "summary", xlim = c(0,1))
```

##frequent words in topics
```{r}
plot(communicationfit, type = "labels", topics = c(3,4))

```

##histrogram of topics
```{r}
plot(communicationfit, type = "hist")
```

##comparison of two topics
```{r}
plot(communicationfit, type = "perspectives", topics = c(2,4))
```

##evaluate
```{r}
communicationSelect <- selectModel(out$documents, out$vocab, K=10, prevalence = ~cooperation+round, max.em.its=30, data = meta, runs=20, seed=8458159)
```

##plot different models
```{r}
plotModels(communicationSelect)

```

##plot topic quality
```{r}
topicQuality(model = communicationfit, documents = docs)

```

##exemplary quote
```{r}
**https://rdrr.io/cran/stm/man/findThoughts.html
thoughts3 <- findThoughts(communicationfit, n=3, topics=3)$docs[[1]]
plotQuote(thoughts3, width=40, main="Topic 3")
```


##choose model 1
```{r}
selectModel1 <- communicationSelect$runout [[1]]
```

##understand
```{r}
labelTopicSel <- labelTopics(poliblogPrevFit, c(3,20))
print(sageLabels(poliblogPrevFit))
```

##estimation
```{r}
out$meta$rating <- as.factor(out$meta$rating)
prep <- estimateEffect(1:5 ~ treatment, communicationfit, meta=out$meta, 
                       uncertainty="Global")
```

##plotting
```{r}
plot(prep, covariate="treatment", topics=c(3,4), model=communicationfit, method = "difference", cov.value1 = "0", cov.value2 = "2", xlab =  "complete information ... competing hydrology", main = "communication and treatment", xlim = c(-0.5,.5), labeltype = "custom", custom.labels = c("strategy_building","longterm_perspecive"))
                                                                                
```
okay. I might need to lag a variable because communication in round 1 should affect crop choice in round 2. 

##how prevalence of topics differ across values of a continuous covariate
```{r}
plot(prep, "round", method="continuous", topics=3, model=z, printlegend=FALSE, xaxt="n", 
     xlab="round (1-10)")
**need better specification
roundseq <- seq(from=as.Date("1"), to=as.Date("10"), by="round")
monthnames <- months(monthseq)
axis(1, at=as.numeric(monthseq)-min(as.numeric(monthseq)), labels=monthnames)
```

##topic corelation
```{r}
mod.out.corr <- topicCorr(communicationfit)
plot(mod.out.corr)
```

##
```{r}
communicationContent <- stm(out$documents, out$vocab, K=5, prevalence=~cooperation+round, 
                       content=~cooperation, max.em.its=75, data=out$meta, 
                       init.type="Spectral", seed=8458159)
plot(communicationContent, type="perspectives", topics = 4)
```

##interaction effect
```{r}
poliblogInteraction <- stm(out$documents, out$vocab, K=10, prevalence=~rating*day, 
                           max.em.its=10, data=out$meta, seed=8458159)
```

##plot interaction
```{r}
prep2 <- estimateEffect(c(10) ~ rating*day, poliblogInteraction, metadata=out$meta, 
                        uncertainty="None")
plot(prep2, covariate="day", model=poliblogInteraction, method="continuous", xlab="Days",
     moderator="rating", moderator.value="Liberal", linecol="blue", ylim=c(0,0.12), 
     printlegend=F)
plot(prep2, covariate="day", model=poliblogInteraction, method="continuous", xlab="Days",
     moderator="rating", moderator.value="Conservative", linecol="red", add=T,
     printlegend=F)
legend(0,0.12, c("Liberal", "Conservative"), lwd=2, col=c("blue", "red"))

```
