---
title: "stmgame"
author: "minwoo ahn"
date: "2023-08-03"
output: html_document
------
```{r}
knitr::opts_chunk$set(echo = TRUE)
```
##https://github.com/dondealban/learning-stm

1. Groundwater Game
##lag communication
```{r}
library(dplyr)

#add new column that shows sales for previous day
GGcommunicationdataset_mw_060723$lag_communication <- dplyr::lag(GGcommunicationdata_mw_060723$text)

```

## stm installation
```{r}
library(stm)
library (igraph)
library (stmCorrViz)
```

##open in Window or MAC
```{r}
##revise the code as necessary
data <- read.csv("GGcommunicationdata_mw_060723.csv")
```

##stemming and stopword removal
```{r}
processed <- textProcessor(GGcommunicationdataset_mw_062723$text, metadata = GGcommunicationdataset_mw_062723)
```

##structure and index the data for usage in the stm
```{r}
out <- prepDocuments(processed$documents, processed$vocab, processed$meta)
```

##save the output object meta, documents, and vocab into variables
```{r}
docs <- out$documents
vocab <- out$vocab
meta <- out$meta
```

##check removed words and documents
```{r}
plotRemoved(processed$documents, lower.thresh = seq(1,200, by=100))
```

##estimation (1).prevalance of topics across documents' meta data
```{r}
communicationfit <- stm(out$documents, out$vocab, K=5, prevalence = ~treatment, data = out$meta, max.em.its=75, init.type = "Spectral", seed = 8458150)

communicationfit2 <- stm(out$documents, out$vocab, K=5, prevalence = ~cooperation+round, data = out$meta, max.em.its=75, init.type = "Spectral", seed = 8458150)

```
##plot the model
```{r}
plot(communicationfit, type = "summary", xlim = c(0,1))
plot(communicationfit2, type = "summary", xlim = c(0,1))
```

##frequent words in topics
```{r}
plot(communicationfit, type = "labels", topics = c(3,4))
plot(communicationfit2, type = "labels", topics = c(3,4))

```

##histrogram of topics
```{r}
plot(communicationfit, type = "hist")
plot(communicationfit2, type = "hist")
```

##comparison of two topics
```{r}
plot(communicationfit, type = "perspectives", topics = c(2,4))
plot(communicationfit, type = "perspectives", topics = c(1,4))
```

##evaluate
```{r}
communicationSelect <- selectModel(out$documents, out$vocab, K=10, prevalence = ~cooperation+round, max.em.its=30, data = meta, runs=20, seed=8458159)
```

##plot different models
```{r}
plotModels(communicationSelect)

```

##plot topic quality
```{r}
topicQuality(model = communicationfit, documents = docs)
topicQuality(model = communicationfit2, documents = docs)
```

##label top words
```{r}
labelTopicsSel <- labelTopics(communicationfit, c(1,3,4))
print(sageLabels(communicationfit))
```

##exemplary quote
```{r}
thoughts3 <- findThoughts(communicationfit, texts=text, n=3, topics=3)$docs[[1]]
plotQuote(thoughts3, width=40, main="Topic 3")
```


##choose model 3
```{r}
selectModel1 <- communicationSelect$runout [[1]]
```

##estimation
```{r}
out$meta$rating <- as.factor(out$meta$rating)
prep <- estimateEffect(1:5 ~ treatment, communicationfit, meta=out$meta, uncertainty="Global")
prep1 <- estimateEffect(1:5 ~ cooperation+round, communicationfit2, meta=out$meta, uncertainty="Global")

```

##plotting 1. the effect of scientific uncertainty on communication strategies
```{r}
plot(prep, covariate="treatment", topics=c(3,4), model=communicationfit, method = "difference", cov.value1 = "0", cov.value2 = "2", xlab =  "complete information ... competing hydrology", main = "communication and treatment", xlim = c(-0.5,.5), labeltype = "custom", custom.labels = c("strategy_building","longterm_perspecive"))
                                                                                
```
##plotting 2. the effect of communication on cooperation
```{r}
plot(prep1, covariate="cooperation", topics = c(1,2,3,4,5), model=communicationfit, method = "difference", cov.value1 = "0", cov.value2 = "1", xlab = "less cooperation ... more cooperation", main = "The effects of communication on cooperation", xlim = c(-0.5,.5), labeltype = "custom", custom.labels = c("strategy1", "strategy2", "strategy3", "strategy4", "strategy5"))
```

##how prevalence of topics differ across values of a continuous covariate
```{r}
plot(prep1, "round", method="continuous", topics=3, model=z, printlegend=FALSE, xaxt="n", 
     xlab="round (1-10)")
```

##topic corelation
```{r}
mod.out.corr <- topicCorr(communicationfit)
plot(mod.out.corr)
mod.out.corr <- topicCorr(communicationfit2)
plot(mod.out.corr)
```
